---
title: "Our Project- 
Drinking in 'How I Met Your Mother'"
subtitle:  "Mays, Shai & Shir"
runtime: shiny
output: tufte::tufte_html

---

As part of our project, we decided to analyze and visualize the drinking patterns on our favorite American sitcom, "How I Met Your Mother," throughout the sessions.

We counted the words associated with drinking in each episode based on the script of the series, and then visualized the results, as you can see:


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman:: p_load(rvest, tidyverse,stringr, tidytext, raster)
library(ggplot2)
library(plotly)
library(hrbrthemes)
library(shiny)
library(dplyr)


setwd("C:/Users/shiri/OneDrive/Desktop/Shir/matan")
  
```


```{r eval=FALSE}

#The first part of our script is based on:
#Jorge Cimentada's previous work (https://cimentadaj.github.io/blog/)

main_url <- "http://transcripts.foreverdreaming.org"
all_pages <- paste0("http://transcripts.foreverdreaming.org/viewforum.php?f=177&start=", seq(0, 200, 25))
characters <- c("ted", "lily", "marshall", "barney", "robin")
drink <- c("beer","beers", "drink", "drinks", "drinking", "drunk", "cheers", "champagne",
           "whiskey", "bar", "bars", "pub", "pubs", "wine", "wines", "shot", "shots")

episode_getter <- function(link) {
  title_reference <-
    link %>%
    read_html() %>%
    html_nodes(".topictitle") # Get the html node name with 'selector gadget'
  
  episode_links <-
    title_reference %>%
    html_attr("href") %>%
    gsub("^.", "", .) %>%
    paste0(main_url, .) %>%
    setNames(title_reference %>% html_text()) %>%
    enframe(name = "episode_name", value = "link")
  
  episode_links
}

all_episodes <- map_df(all_pages, episode_getter) # loop over all seasons and get all episode links
all_episodes$id <- 1:nrow(all_episodes)

episode_fun <- function(file) {
  
  file %>%
    read_html() %>%
    html_nodes(".postbody") %>%
    html_text() %>%
    str_split("\n|\t") %>%
    .[[1]] %>%
    data_frame(text = .) %>%
    filter(str_detect(text, ""), # Lots of empty spaces
           !str_detect(text, "^\\t"), # Lots of lines with \t to delete
           !str_detect(text, "^\\[.*\\]$"), # Text that start with brackets
           !str_detect(text, "^\\(.*\\)$"), # Text that starts with parenthesis
           str_detect(text, "^*.:"), # I want only lines with start with dialogue (:)
           !str_detect(text, "^ad")) # Remove lines that start with ad (for 'ads', the link of google ads)
}

all_episodes$text <- map(all_episodes$link, episode_fun)
all_episodes$count <- map_dbl(all_episodes$text, nrow)

all_episodes <-
  all_episodes %>%
  separate(episode_name, c("season", "episode"), "-", extra = "merge") %>%
  separate(season, c("season", "episode_number"), sep = "x")

lines_characters <-
  map(filter(all_episodes, count > 100) %>% pull(text), ~ { 
    # only loop over episodes that have over 10 lines
    .x %>%
      separate(text, c("character", "text"), sep = ":", extra = 'merge') %>%
      # separate character dialogue from actual dialogo
      unnest_tokens(character, character) %>%
      filter(str_detect(character, paste0(paste0("^", characters, "$"), collapse = "|"))) %>%
      # only count the lines of our chosen characters
      mutate(episode_lines_id = 1:nrow(.))
  }) %>%
  setNames(filter(all_episodes, count > 100) %>% # name according to episode
             unite(season_episode, season, episode_number, sep = "x") %>%
             pull(season_episode)) %>%
  enframe() %>%
  unnest() %>%
  mutate(all_lines_id = 1:nrow(.))

words_per_character <-
  lines_characters %>%
  unnest_tokens(word, text) %>% # expand all sentences into words
  anti_join(stop_words) %>% # remove bad words
  filter(!word %in% characters) %>% # only select characters we're interested
  arrange(name) %>%
  separate(name, c("season", "episode"), sep = "x", remove = FALSE) %>%
  mutate(name = factor(name, ordered = TRUE),
         season = factor(season, ordered = TRUE),
         episode = factor(episode, ordered = TRUE)) %>%
  filter(season != "07")

```

```{r eval=FALSE}

words_per_character$count <- 0

for (i in drink) {
  for (j in 1:nrow(words_per_character)) 
    {
    words_per_character[j,8] <- 
      ifelse(words_per_character[j,7] == i, words_per_character[j,8] +1 , words_per_character[j,8])
  }
}

words_per_character$season_episode <- (as.numeric(words_per_character$season)
+ (as.numeric(words_per_character$episode) /10))

#creating data for the plot
plot_data <- words_per_character %>%     
  group_by(season_episode) %>%          
  summarise_at(vars(count),             
               list(drink_words_per_episode = sum))
write.csv(plot_data, "data_for_shiny.csv")


plot_data_new <- plot_data %>% separate(season_episode, c('season', 'episode'))
plot_data_new <- na.omit(plot_data_new)
write.csv(plot_data_new, "data_for_shiny2.csv")
```


```
---
runtime: shiny
---
```

## Inputs and Outputs

```{r ex_inputs}
#| eval = FALSE
inputPanel(
  
  sliderInput("season", label = "Select season:",
              min = 1, max = 8, value = 4, step = 1)
)
```


```{r}
data2 <- read.csv("data_for_shiny.csv")

data2 |> ggplot(aes(x= season_episode , y= drink_words_per_episode)) +
  geom_area(fill="#69b3a2", alpha=0.5) +
  geom_line(color="#69b3a2") +
  ylab("Drinking (words)") +
  xlab("Episodes Across The Season")

```


# integration with shiny
```{r ex_render}
#| eval = FALSE

renderPlot({
    data2 <- read.csv("data_for_shiny2.csv")
    data2 <- data2 %>% dplyr::filter(season == input$season)

data2 |> ggplot(aes(x= episode , y= drink_words_per_episode)) +
  geom_area(fill="#69b3a2", alpha=0.5) +
  geom_line(color="#69b3a2") +
  ylab("Drinking (words)") +
  xlab("Episodes Across The Season")
})
```

This is what this looks like!!! :)

```{r ex, ref.label=c("ex_inputs", "ex_render")}
#| eval=TRUE,
#| echo=FALSE
```

